---
title: 'Playoffs 2: NBA Predictions'
author: "Rohan Venkatraman"
date: "2023-03-07"
output: html_document
---

```{r setup, warnings=FALSE,message=FALSE include=FALSE}
library(readr)
library(dplyr)
library(tidyr)
library(scales)
library(DT)
library(kableExtra)
library(ggplot2)
library(data.table)
library(magrittr)
library(nbastatR)
```

# Import New Data

## API to pull from NBA Advanced Stats
```{r}
headers = c(
  `Connection` = 'keep-alive',
  `Accept` = 'application/json, text/plain, */*',
  `x-nba-stats-token` = 'true',
  `DNT` = '1',
  `User-Agent` = 'Mozilla/5.0 (Windows NT 10.0; Win64; x64) AppleWebKit/537.36 (KHTML, like Gecko) Chrome/94.0.4606.81 Safari/537.36',
  `x-nba-stats-origin` = 'stats',
  `Sec-GPC` = '1',
  `Origin` = 'https://www.nba.com',
  `Sec-Fetch-Site` = 'same-site',
  `Sec-Fetch-Mode` = 'cors',
  `Sec-Fetch-Dest` = 'empty',
  `Referer` = 'https://www.nba.com/',
  `Accept-Language` = 'en-US,en;q=0.9',
  `If-Modified-Since` = 'Wed, 08 Mar 2023 23:24:06 GMT'
)
```

### Advanced Stats Data Set
```{r}
params = list(
  `Conference` = '',
  `DateFrom` = '',
  `DateTo` = '',
  `Division` = '',
  `GameScope` = '',
  `GameSegment` = '',
  `LastNGames` = '0',
  `LeagueID` = '00',
  `Location` = '',
  `MeasureType` = 'Advanced',
  `Month` = '0',
  `OpponentTeamID` = '0',
  `Outcome` = '',
  `PORound` = '0',
  `PaceAdjust` = 'N',
  `PerMode` = 'PerGame',
  `Period` = '0',
  `PlayerExperience` = '',
  `PlayerPosition` = '',
  `PlusMinus` = 'N',
  `Rank` = 'N',
  `Season` = '2022-23',
  `SeasonSegment` = '',
  `SeasonType` = 'Regular Season',
  `ShotClockRange` = '',
  `StarterBench` = '',
  `TeamID` = '0',
  `TwoWay` = '0',
  `VsConference` = '',
  `VsDivision` = ''
)

res <- httr::GET(url = 'https://stats.nba.com/stats/leaguedashteamstats', httr::add_headers(.headers=headers), query = params)
data <- httr::content(res) %>% .[['resultSets']] %>% .[[1]]
column_names <- data$headers %>% as.character()  
Team_Adv_Stats <- rbindlist(data$rowSet) %>% setnames(column_names)

rm(res, data, column_names, params)
```

### Advanced Defensive Stats Data Set
```{r}
params = list(
  `Conference` = '',
  `DateFrom` = '',
  `DateTo` = '',
  `Division` = '',
  `GameScope` = '',
  `GameSegment` = '',
  `LastNGames` = '0',
  `LeagueID` = '00',
  `Location` = '',
  `MeasureType` = 'Four Factors',
  `Month` = '0',
  `OpponentTeamID` = '0',
  `Outcome` = '',
  `PORound` = '0',
  `PaceAdjust` = 'N',
  `PerMode` = 'PerGame',
  `Period` = '0',
  `PlayerExperience` = '',
  `PlayerPosition` = '',
  `PlusMinus` = 'N',
  `Rank` = 'N',
  `Season` = '2022-23',
  `SeasonSegment` = '',
  `SeasonType` = 'Regular Season',
  `ShotClockRange` = '',
  `StarterBench` = '',
  `TeamID` = '0',
  `TwoWay` = '0',
  `VsConference` = '',
  `VsDivision` = ''
)

res <- httr::GET(url = 'https://stats.nba.com/stats/leaguedashteamstats', httr::add_headers(.headers=headers), query = params)
data <- httr::content(res) %>% .[['resultSets']] %>% .[[1]]
column_names <- data$headers %>% as.character()  
Team_Factors_Stats <- rbindlist(data$rowSet) %>% setnames(column_names)

rm(res, data, column_names, params)
```

### Advanced Four Factors Stats Data Set
```{r}
params = list(
  `Conference` = '',
  `DateFrom` = '',
  `DateTo` = '',
  `Division` = '',
  `GameScope` = '',
  `GameSegment` = '',
  `LastNGames` = '0',
  `LeagueID` = '00',
  `Location` = '',
  `MeasureType` = 'Defense',
  `Month` = '0',
  `OpponentTeamID` = '0',
  `Outcome` = '',
  `PORound` = '0',
  `PaceAdjust` = 'N',
  `PerMode` = 'PerGame',
  `Period` = '0',
  `PlayerExperience` = '',
  `PlayerPosition` = '',
  `PlusMinus` = 'N',
  `Rank` = 'N',
  `Season` = '2022-23',
  `SeasonSegment` = '',
  `SeasonType` = 'Regular Season',
  `ShotClockRange` = '',
  `StarterBench` = '',
  `TeamID` = '0',
  `TwoWay` = '0',
  `VsConference` = '',
  `VsDivision` = ''
)

res <- httr::GET(url = 'https://stats.nba.com/stats/leaguedashteamstats', httr::add_headers(.headers=headers), query = params)
data <- httr::content(res) %>% .[['resultSets']] %>% .[[1]]
column_names <- data$headers %>% as.character()  
Team_Defense_Stats <- rbindlist(data$rowSet) %>% setnames(column_names)

rm(res, data, column_names, params)
```

### NBASTATR Data Set
```{r, warning=FALSE, message=FALSE}
Sys.setenv("VROOM_CONNECTION_SIZE" = 131072 * 2)

#Get NBA Teams
Teams=nba_teams(league="NBA") %>%
  filter(yearPlayedLast==2022,idLeague==2) %>%
  select(nameTeam,idTeam,slugTeam)

#Game Data for 2023
Games2023=game_logs(
  seasons = 2023,
  league = "NBA",
  result_types = "team",
  season_types = "Regular Season",
  nest_data = F,
  assign_to_environment = TRUE,
  return_message = TRUE
)
```
### Team Basic Stats
```{r, warning=FALSE}
Games2023_new <- Games2023 %>% group_by(nameTeam) %>% summarise_all(mean) %>% select(-c(2:22)) %>% select(-c(9, 13, 25, 26))
```

# Cleaning

## Clean Games Dataset
```{r}
# Not necessary to use because data is not new, use nbastatr dataset

# Games <- read.csv("Games.csv", header=TRUE)
# Games = Games %>% select(-c('GAME_STATUS_TEXT', 'TEAM_ID_home', 'TEAM_ID_away'))
# 
# Games <- filter(Games, SEASON == 2022) %>% 
#           merge(Teams, by.x = 'HOME_TEAM_ID', by.y = 'TEAM_ID')
# Games <- merge(Games, Teams, by.x = "VISITOR_TEAM_ID", by.y = "TEAM_ID")
# Games <- rename(Games, "TEAM_ABV_home" = "ABBREVIATION.x",
#                 "TEAM_ABV_away" = "ABBREVIATION.y",
#                 "TEAM_NAME_home" = "NICKNAME.x",
#                 "TEAM_NAME_away" = "NICKNAME.y",
#                 "TEAM_ID_home" = "HOME_TEAM_ID",
#                 "TEAM_ID_away" = "VISITOR_TEAM_ID")
```

```{r}
# Teams dataset not necessary because of nbastatr teams dataset

# Teams2 <- read.csv("Teams.csv", header=TRUE)
# Teams2 = Teams2 %>% select(c('TEAM_ID', 'ABBREVIATION', 'NICKNAME'))
```

## Combine Home and Away Teams for Games (nbastatr)
```{r}
Games2023 <- Games2023 %>% select(-c("yearSeason", "slugSeason", "slugLeague", "typeSeason", "countDaysNextGameTeam", "slugMatchup", "slugOpponent", "slugTeamWinner", "slugTeamLoser", "outcomeGame", "hasVideo", "urlTeamSeasonLogo"))

Home_Games <- Games2023 %>% group_by(idGame) %>% filter(locationGame == 'H')
names(Home_Games) <- paste0(names(Home_Games), '_home')
Away_Games <- Games2023 %>% group_by(idGame) %>% filter(locationGame == 'A')
names(Away_Games) <- paste0(names(Away_Games), '_away')

Combined_Games <- Home_Games %>% merge(Away_Games, by.x="idGame_home", by.y="idGame_away")
Combined_Games <- Combined_Games %>% select(-c("dateGame_away", "isWin_away", "plusminusTeam_away", "minutesTeam_away"))
Combined_Games <- Combined_Games %>% rename("dateGame" = "dateGame_home", 
                                            "Spread" = "plusminusTeam_home", 
                                            "minutes" = "minutesTeam_home") %>% mutate(pts_Total = ptsTeam_home + ptsTeam_away,
                                                                                       oreb_Total = orebTeam_home + orebTeam_away,
                                                                                       isWin_home = ifelse(isWin_home == TRUE, 1, 0),
                                                                                       isOT = ifelse(minutes > 240, 1, 0))
```

### Keep only stat variables from combined data set
```{r}
Combined_Games_Stats <- Combined_Games %>% select(-c(numberGameTeamSeason_home, numberGameTeamSeason_away, isB2B_home, isB2BFirst_home, isB2BSecond_home, isB2B_away,
                                                     isB2BFirst_away, isB2BSecond_away, locationGame_home, locationGame_away
                                                     ))
```

## Player Data Set Cleaning
```{r, warning=FALSE, message=FALSE}
Game_IDs_2023 = Home_Games$idGame_home
# May be better to use an API to pull in recent player data
Player_log <- read.csv("Games_Details.csv", header=TRUE)
Player_log <- Player_log %>% select(-c('NICKNAME', 'COMMENT'))
Player_log <- filter(Player_log, GAME_ID %in% Game_IDs_2023)
Player_log <- Player_log[nzchar(Player_log$MIN), ] # removes rows where players do not play so averages are not affected

Player_log$MIN <- sapply(strsplit(Player_log$MIN, ":"), function(x) sum(as.numeric(x) * c(1, 1/60)))
Player_log_grouped <- Player_log %>% group_by(TEAM_ID, TEAM_ABBREVIATION, PLAYER_ID, PLAYER_NAME) %>% summarise(MIN_mean = mean(MIN),
                                                                                                                FGM = sum(FGM),
                                                                                                                FGA = sum(FGA),
                                                                                                                FG_PCT = FGM / FGA,
                                                                                                                FG3M = sum(FG3M),
                                                                                                                FG3A = sum(FG3A),
                                                                                                                FG3_PCT = FG3M / FG3A,
                                                                                                                FTM = sum(FTM),
                                                                                                                FTA = sum(FTA),
                                                                                                                FT_PCT = FTM / FTA,
                                                                                                                PLUS_MINUS_mean = mean(PLUS_MINUS),
                                                                                                                OREB_mean = mean(OREB),
                                                                                                                DREB_mean = mean(DREB),
                                                                                                                REB_mean = mean(REB),
                                                                                                                AST_mean = mean(AST),
                                                                                                                STL_mean = mean(STL),
                                                                                                                BLK_mean = mean(BLK),
                                                                                                                TO_mean = mean(TO),
                                                                                                                PF_mean = mean(PF),
                                                                                                                PTS_mean = mean(PTS)
                                                                                                              )
```

## Cleaning Advanced Stats Data Sets
```{r}
Team_Adv_Stats <- select(Team_Adv_Stats, -c(28:46))
Team_Defense_Stats <- select(Team_Defense_Stats, -c(17:30))
Team_Factors_Stats <- select(Team_Factors_Stats, -c(16:28))
```

# New Variable Creation
```{r}
Combined_Games_Stats <- Combined_Games_Stats %>% mutate(Fatigue_Diff = countDaysRestTeam_home - countDaysRestTeam_away)
Home_Games_Summary <- Home_Games %>% group_by(nameTeam_home) %>% mutate(isWin_home = ifelse(isWin_home == TRUE, 1, 0)) %>% summarise(W_Pct_Home = sum(isWin_home) / n())
Away_Games_Summary <- Away_Games %>% group_by(nameTeam_away) %>% mutate(isWin_home = ifelse(isWin_away == TRUE, 1, 0)) %>% summarise(W_Pct_Away = sum(isWin_away) / n())

Home_Games_Summary2 <- Combined_Games_Stats %>% group_by(nameTeam_home) %>% summarise(Outscoring = mean(Spread))
Away_Games_Summary2 <- Combined_Games_Stats %>% group_by(nameTeam_away) %>% summarise(Outscored = mean(Spread))
Home_Court_Adv <- merge(Home_Games_Summary2, Away_Games_Summary2, by.x = 'nameTeam_home', by.y = 'nameTeam_away') %>% mutate(HCA = Outscoring - Outscored)

Team_Adv_Stats <- merge(Team_Adv_Stats, Home_Court_Adv, by.x = 'TEAM_NAME', by.y = 'nameTeam_home')
```


# Create Master Dataset
```{r}
NBA_Master<- merge(Games2023_new, Team_Adv_Stats, by.x = 'nameTeam', by.y = 'TEAM_NAME')
NBA_Master <- merge(NBA_Master, Team_Defense_Stats, by.x = 'nameTeam', by.y = 'TEAM_NAME')
NBA_Master <- merge(NBA_Master, Team_Factors_Stats, by.x = 'nameTeam', by.y = 'TEAM_NAME')

cols_to_delete <- grep("\\.y$", names(NBA_Master))
NBA_Master <- NBA_Master[, -cols_to_delete]
cols_to_delete <- grep("\\.x$", names(NBA_Master))
NBA_Master <- NBA_Master[, -cols_to_delete]

NBA_Master <- NBA_Master %>% relocate(c('nameTeam', 'TEAM_ID','GP','W', 'L', 'MIN', 'W_PCT', 'W_Pct_Home', 'W_Pct_Away'))
```

